Uni- and Multivariate Analysis of Dendritic Ca2+ Data

### 2017-07-19 presentation/demo.tex
asd

\section{Goal}
\begin{frame}[fragile]{Goal}
The goal of this project is to investigate the following:
\begin{itemize}
\only<+->{
\item What is the relationship between Ca2+ activity and stimulus intensity/behavior}
\only<+->{
\item Does a multivariate approach give us any significant advantage over a univariate one?}
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{SVM - What is an SMV?}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.3\textwidth]{svm_exp1.png}
	\end{figure}}
	\only<+->{
	\begin{figure}
      \includegraphics[height=0.3\textwidth]{svm_exp.png}
	\end{figure}}
	\end{center}
\end{frame}

@@

@@

@@

\begin{frame}[fragile]{Optimal Averaging Times}
\begin{center}
	\begin{figure}
	\caption*{Dummy}
      \includegraphics[width=0.6\textwidth]{placeholder_wind_pres.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{Optimal Averaging Times - Behavior}
\begin{center}
	\begin{figure}
	\caption*{Dummy}
      \includegraphics[width=0.6\textwidth]{placeholder_wind_hit.png}
	\end{figure}
	\end{center}
\end{frame}

>>>>

\section{Goal}
\begin{frame}[fragile]{Goal}
The goal of this project is to investigate the following:
\begin{itemize}
\only<+->{
\item What is the relationship between Ca2+ activity and stimulus intensity/behavior}
\only<+->{
\item Can we build good classifiers for this data?}
\only<+->{
\item Does a multivariate approach give us any significant advantage over a univariate one?}
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{SVM - What is an SMV?}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.3\textwidth]{svm_exp1.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
	\begin{columns}[T,onlytextwidth]
    \column{0.5\textwidth}
    	\only<+->{
      \begin{figure}
      \includegraphics[height=0.7\textwidth]{svm_exp2.png}
      \end{figure}}

    \column{0.5\textwidth}
		\only<+->{
      \begin{figure}
      \includegraphics[height=0.7\textwidth]{svm_exp3.png}
      \end{figure}}

@@

\begin{frame}[fragile]{SVM - Numbers of Classifying Dendrites by Stimulus}
\begin{center}
	\begin{figure}
      \includegraphics[width=1.0\textwidth]{n_acc.png}
	\end{figure}
	\end{center}
\end{frame}

@@

\begin{frame}[fragile]{Timing - What if we use different Averaging Windows?}
So far we have always averaged over the first second after the stimulus. \newline

What if we average over the second before or the second second after the stimulus?
\end{frame}

\begin{frame}[fragile]{Statistical Significance - Stimulus Presence}
\begin{center}
	\begin{figure}
      \includegraphics[width=1.0\textwidth]{statsig.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{Statistical Significance - Behavior}
At threshold stimulus $\approx$ 1
\begin{center}
	\begin{figure}
      \includegraphics[width=1.0\textwidth]{statsig_b.png}
	\end{figure}
	\end{center}
\end{frame}

@@
